Tackling discrepancies in freshwater invertebrate trait databases: Harmonising across continents and aggregating taxonomic resolution

### 2021-02-18 Paper/Results/SI.tex
15.02.: Small edits
18.02: Formatting fixes

    \begin{longtable}{m{1.8cm}|m{3cm}|m{3cm}|m{3cm}|m{3cm}|m{3.2cm}|m{3cm}}

@@

        Multivoltine & 

@@

    \begin{minipage}{\linewidth}\small

@@

@@

\begin{table}[ht]
    \centering
    \caption{Mean, median and standard deviation of the affinities of traits that were responsive to the salinity gradient in the original study but not in the re-analysis using the harmonised European trait dataset.} 
    \label{tab:SI_resp_traits_summary_stats}
    \begin{tabular}{llccc|c}
    \toprule[.1em]
    Type & Trait & Mean & Median & SD & Responsive? \\ 
    \toprule[.1em]
    Stepw\_median & Shredder & 0.20 & 0.14 & 0.25 & No \\ 
      Stepw\_mean & Shredder & 0.18 & 0.12 & 0.22 & No\\ 
      Direct\_median & Shredder & 0.21 & 0.14 & 0.25 & No\\ 
      Direct\_mean & Shredder & 0.19 & 0.14 & 0.22 & No\\ 
      Weighted & Shredder & 0.19 & 0.14 & 0.22 & No \\ 
      Harmonised; not\_aggregated & Shredder & 0.18 & 0.12 & 0.24 & No \\ 
      Original & Shredder & 0.25 & 0.14 & 0.32 & Yes\\ 
      \midrule
      Stepw\_median & Gills & 0.30 & 0.27 & 0.32 & Yes\\ 
      Stepw\_mean & Gills & 0.29 & 0.22 & 0.32 & Yes\\ 
      Direct\_median & Gills & 0.30 & 0.30 & 0.32 & Yes\\ 
      Direct\_mean & Gills & 0.30 & 0.30 & 0.32 & Yes\\ 
      Weighted & Gills & 0.30 & 0.30 & 0.32 & Yes\\ 
      Harmonised; not\_aggregated & Gills & 0.30 & 0.25 & 0.32 & No \\ 
      Original & Gills & 0.28 & 0.00 & 0.33 & Yes \\ 
      \midrule
      Stepw\_median & Short life cycle & 0.64 & 0.75 & 0.39 & No \\ 
      Stepw\_mean & Short life cycle & 0.64 & 0.79 & 0.39 & No \\ 
      Direct\_median & Short life cycle & 0.67 & 0.75 & 0.37 & Yes \\ 
      Direct\_mean & Short life cycle & 0.67 & 0.79 & 0.38 & Yes \\ 
      Weighted & Short life cycle & 0.67 & 0.79 & 0.38 & Yes\\ 
      Harmonised; not\_aggregated & Short life cycle & 0.64 & 0.75 & 0.40 & Yes \\ 
      Original & Short life cycle & 0.64 & 0.75 & 0.40 & Yes \\ 
      \midrule
      Stepw\_median & Long life cylce & 0.36 & 0.25 & 0.39 & No \\ 
      Stepw\_mean & Long life cylce & 0.36 & 0.21 & 0.39 & No \\
      Direct\_median & Long life cylce & 0.33 & 0.25 & 0.37 & Yes\\ 
      Direct\_mean & Long life cylce & 0.33 & 0.21 & 0.38 & Yes \\ 
      Weighted & Long life cylce & 0.33 & 0.21 & 0.38 & Yes \\ 
      Harmonised; not\_aggregated & Long life cylce & 0.36 & 0.25 & 0.40 & Yes \\ 
      Original & Long life cylce & 0.36 & 0.25 & 0.40 & Yes\\ 
    \bottomrule
    \end{tabular}
\end{table}

\begin{figure}[ht]
    \centering
    \includegraphics[width=18.5cm, height=16cm]{boxplot_scores_combined_REMAIN_SI.png}
    \caption{RDA of traits constrained by electric conductivity for the data aggregated with \textit{direct\_agg \textsubscript{mean}}, \textit{stepwise\_agg \textsubscript{mean}}, and \textit{weighted\_agg}. Shown are boxplots of the site scores along the conductivity axis. The rug on the right side of each plot indicates species scores of the traits on the conductivity axis. For more details see Figure \ref{fig:boxplot_scores_on_constrained_axis}. lcd, life cycle duration; nr.cy, potential number of cycles per year.}
    \label{fig:boxplots_scores_on_constrained_axis_REMAIN}
\end{figure}
%   \clearpage % insert a page break
%   \captionof{figure}{RDA of traits constrained by electric conductivity for the tested methods and the original study. Shown are boxplots of the site scores along the conductivity axis. The rug on the right side of each plot indicates species scores of the traits on the conductivity axis. Only traits with a Mahalanobis distance greater than the $97.5 \%$ quantile of the Chi-square distribution (5.02) were labelled. For better comparability, species scores of the original analysis were multiplied by -1.}

>>>>

    \begin{longtable}{m{1.9cm}|m{3.3cm}|m{3.3cm}|m{2.7cm}|m{3cm}|m{3.2cm}|m{2.5cm}}

@@

        Multi\-voltine & 

@@

    \begin{minipage}{\linewidth}{\fontsize{8}{10}\selectfont

@@

        }

@@

\begin{table}[ht]
    \centering
    \caption{Mean, median and standard deviation of the affinities of traits that were responsive to the salinity gradient in the original study but not in the re-analysis using the harmonised European trait dataset.} 
    \label{tab:SI_resp_traits_summary_stats}
    \begin{tabular}{l|l|c|c|c|c}
    \toprule[.1em]
    Type & Trait & Mean & Median & SD & Responsive? \\ 
    \toprule[.1em]
    Stepw\_median & Shredder & 0.20 & 0.14 & 0.25 & No \\ 
      Stepw\_mean & Shredder & 0.18 & 0.12 & 0.22 & No\\ 
      Direct\_median & Shredder & 0.21 & 0.14 & 0.25 & No\\ 
      Direct\_mean & Shredder & 0.19 & 0.14 & 0.22 & No\\ 
      Weighted & Shredder & 0.19 & 0.14 & 0.22 & No \\ 
      Harmonised; not\_aggregated & Shredder & 0.18 & 0.12 & 0.24 & No \\ 
      Original & Shredder & 0.25 & 0.14 & 0.32 & Yes\\ 
      \midrule
      Stepw\_median & Gills & 0.30 & 0.27 & 0.32 & Yes\\ 
      Stepw\_mean & Gills & 0.29 & 0.22 & 0.32 & Yes\\ 
      Direct\_median & Gills & 0.30 & 0.30 & 0.32 & Yes\\ 
      Direct\_mean & Gills & 0.30 & 0.30 & 0.32 & Yes\\ 
      Weighted & Gills & 0.30 & 0.30 & 0.32 & Yes\\ 
      Harmonised; not\_aggregated & Gills & 0.30 & 0.25 & 0.32 & No \\ 
      Original & Gills & 0.28 & 0.00 & 0.33 & Yes \\ 
      \midrule
      Stepw\_median & Short life cycle & 0.64 & 0.75 & 0.39 & No \\ 
      Stepw\_mean & Short life cycle & 0.64 & 0.79 & 0.39 & No \\ 
      Direct\_median & Short life cycle & 0.67 & 0.75 & 0.37 & Yes \\ 
      Direct\_mean & Short life cycle & 0.67 & 0.79 & 0.38 & Yes \\ 
      Weighted & Short life cycle & 0.67 & 0.79 & 0.38 & Yes\\ 
      Harmonised; not\_aggregated & Short life cycle & 0.64 & 0.75 & 0.40 & Yes \\ 
      Original & Short life cycle & 0.64 & 0.75 & 0.40 & Yes \\ 
      \midrule
      Stepw\_median & Long life cylce & 0.36 & 0.25 & 0.39 & No \\ 
      Stepw\_mean & Long life cylce & 0.36 & 0.21 & 0.39 & No \\
      Direct\_median & Long life cylce & 0.33 & 0.25 & 0.37 & Yes\\ 
      Direct\_mean & Long life cylce & 0.33 & 0.21 & 0.38 & Yes \\ 
      Weighted & Long life cylce & 0.33 & 0.21 & 0.38 & Yes \\ 
      Harmonised; not\_aggregated & Long life cylce & 0.36 & 0.25 & 0.40 & Yes \\ 
      Original & Long life cylce & 0.36 & 0.25 & 0.40 & Yes\\ 
    \bottomrule
    \end{tabular}
\end{table}

\begin{figure}[ht]
    \centering
    \includegraphics[width=18.5cm, height=16cm]{boxplot_scores_combined_REMAIN_SI.png}
    \caption{RDA of traits constrained by electric conductivity for the data aggregated with \textit{direct\_agg \textsubscript{mean}}, \textit{stepwise\_agg \textsubscript{mean}}, and \textit{weighted\_agg}. Shown are boxplots of the site scores along the conductivity axis. The rug on the right side of each plot indicates species scores of the traits on the conductivity axis. For more details see Figure \ref{fig:boxplot_scores_on_constrained_axis}. Abbreviations: lcd, life cycle duration; nr.cy, potential number of cycles per year.}
    \label{fig:boxplots_scores_on_constrained_axis_REMAIN}
\end{figure}
